\cvsection{Hobby Projects}
\cvachievement{\faServer}{Stock Trading Bot.}{
  I have built out a stock trading bot using Alpaca Trading Webhooks and API's, Python, Postgres and Redis. This bot is deployed on Kubernetes through my homelab internal developer platform. The application is made up of 3 components. 
  \begin{itemize}
    \item The API which serves the data. 
    \item The tradestream which is a websocket listener which listens for order events such as fills, cancellations and creations. This is used to improve trade quality with near realtime updates on trading behaviour for a stock.
    \item the datastream which is a websocket listener which listens for trade bars and qoutes and trades. These are used with strategies to buy and sell stocks based on market movements. 
  \end{itemize}
}

\divider
\cvachievement{\faServer}{Homelab Internal Developer Platform.}{ 
  I have been building an Internal Developer Platform on bare metal Kubernetes at home.
  Functionality includes:
  \begin{itemize}
    \item Backups with Velero
    \item Access to internal ( to the cluster ) private services with Wireguard
    \item Secret management with External Secrets and Sealed Secrets
    \item Application provisioning with ArgoCD and FluxCD
    \item Persistent storage management with Ceph Rook
    \item Documentation management with Docusaurus
    \item AWS infrastructure management with Terragrunt
    \item Domain name and certificate management with Route53, MetalLB, External DNS and Cert Manager
    \item Monitoring with Grafana, Loki and Prometheus
    \item Service Mesh with Istio
    \item Authentication with a custom built Identity Provider. Including OIDC authentication with JWT's and session management
    \item OAuth2-Proxy integration with the IDP for plug and play service authentication
    \item An Admin console built in ReactJS to dynamically create secrets, subdomains and manage users, clients, roles and scopes 
  \end{itemize} 
}
